Latent Variable Clustering for Classification of Events in the AT-TPC

### 2020-06-07 doc/Manuscript/article.tex
all plots new

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{plots/display_eventssimulated.pdf}
\caption[Displaying simulated events in 2D and 3D]{Two- and three-dimensional representations of two events from a simulated ${}^{46}$Ar experiment. Each row is one event in two projections, where the color intensity of each point indicates higher charge values recorded by the detector.}\label{fig:sim_samples}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{plots/display_eventsfull_.pdf}
\caption[Displaying un-filtered events in 2D and 3D]{Two- and three-dimensional representations of two events from the ${}^{46}$Ar experiment. Each row is one event in two projections, where the color intensity of each point indicates higher charge values recorded by the detector.}\label{fig:samples}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth, height=9cm]{plots/display_eventsclean_.pdf}
\caption[Displaying filtered events in 2D and 3D]{Two- and three-dimensional representations of two events from the ${}^{46}$Ar experiment. Each row is one event in two projections, where the lightness of each point indicates higher charge values. These events have been filtered with a nearest neighbors algorithm and an algorithm based on the Hough transform, described in section \ref{sec:filtered}}\label{fig:samples_filtered}
\end{figure}

@@

	\subfloat{
	\includegraphics[width=0.5\textwidth]{plots/filtered_mixae_conf_mat.pdf}
}
	\hspace{-1cm}
	\subfloat{
	\includegraphics[width=0.5\textwidth]{plots/full_mixae_conf_mat.pdf}
}
\caption[MIXAE - confusion matrices]{Confusion matrices for the MIXAE clustering algorithm on filtered and full AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:mixae_confmat}
\end{figure}

>>>>

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{custom_work/examples_raw.pdf}
\caption[Displaying un-filtered events in 2D and 3D]{Two- and three-dimensional representations of two events from the ${}^{46}$Ar experiment. Each row is one event in two projections, where the color intensity of each point indicates higher charge values recorded by the detector.}\label{fig:samples}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth, height=9cm]{custom_work/examples_filtered.pdf}
\caption[Displaying filtered events in 2D and 3D]{Two- and three-dimensional representations of two events from the ${}^{46}$Ar experiment. Each row is one event in two projections, where the lightness of each point indicates higher charge values. These events have been filtered with a nearest neighbors algorithm and an algorithm based on the Hough transform, described in section \ref{sec:filtered}}\label{fig:samples_filtered}
\end{figure}

@@

	\includegraphics[width=\textwidth]{custom_work/Filtered_mixae_conf_mat.pdf}

\end{figure}
\begin{figure}[H]
\centering

	\includegraphics[width=\textwidth]{custom_work/Raw_mixae_conf_mat.pdf}

\caption[MIXAE - confusion matrices]{Confusion matrices for the MIXAE clustering algorithm on filtered and full AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:mixae_confmat}
\end{figure}
